Results (Julia)

### 2025-04-30 notebooks/01_results_julia.qmd
update

---
title: Results (Julia)
---

```{julia}
using DrWatson
using Discontinuity
using AlgebraOfGraphics
using DataFramesMeta
using Beforerr
@quickactivate
include("../src/main.jl");
M = var_mapping(; log_str="")

```

@@

```{julia}
# let df = j_events_taus
let df = jno_df, color = r_map, fnames = ["juno_distribution_r", "juno_sw_paramters"]
    spec = data(df) * mapping(; color)
    fs = map([maps1, maps2]) do m
        plot_dist(spec, m; 
            datalimits=datalimits_f,
            axis,
            figure
        )
    end
    resize_to_layout!.(fs)
    easy_save.(fnames, fs)
    display.(fs)
end
```

@@

>>>>

---
title: Results (Julia)
engine: julia
---

```{julia}
using Juno
using Juno: r_map, datalimits_f
using CairoMakie: WilkinsonTicks
using CairoMakie.Makie: resize_to_layout!
using DrWatson
using Discontinuity
using AlgebraOfGraphics
using DataFramesMeta
using Beforerr
import Beforerr: easy_save
using LaTeXStrings
M = var_mapping(; log_str="")

set_aog_theme!()
```

@@

```{julia}
# let df = j_events_taus
let color = r_map, fnames = ["juno_distribution_r", "juno_sw_paramters"]
    df = subset_by_quantiles(udf, [:L_n_cross, :j0_k, :j0_k_norm])
    spec = data(df) * mapping(; color)
    fs = map([maps1, maps2]) do m
        plot_dist(spec, m; 
            datalimits=datalimits_f,
            axis,
            figure
        )
    end
    resize_to_layout!.(fs)
    # easy_save.(fnames, fs)
    display.(fs)
end
```

@@

## Correlation analysis of SWDs observed by 1-AU satellites

Correlation analysis on the current density and solar wind parameters (J-Ne, J-beta, J-|B|, etc.)

```{julia}
using DataStructures: nlargest
let scols = [:j0_k,:j0_k_norm]
    @info "Before subsetting" nlargest.(10, eachcol(wind_df[!, scols]))
    sdf = subset_by_quantiles(wind_df, scols)
    @info "After subsetting"  nlargest.(10, eachcol(sdf[!, scols]))
end
```

```{julia}
using PairPlots

log_df(df) = log.(df)
select_cols(df, cols) = df[!, cols]

begin df = wind_df
    @transform! df :year = year.(:time)
    j_params = ["j0_k", "j0_k_norm", "j_Alfven", "n.mean", "B.mean", "β"]
    cols = intersect(j_params, names(df))
    sdf = subset_by_quantiles(ustrip.(df[!, cols]), Symbol.(cols), lower=0.01, upper=0.99)
    corr_matrix = cor(Matrix(log_df(sdf)))
    @info "Correlation Matrix" corr_matrix

    fig = Figure()
    gs = GridLayout(fig[1,1])
    f = pairplot(gs[1:6,1:6], log_df(sdf))
    # dfs = collect(groupby(df[!, [cols; "year"]], :year))
    # f = pairplot(gs[1:6,2:7], log_df.(select_cols.(dfs, Ref(cols)))..., bottomleft=false, topright=true)
    easy_save("temp/wind_pairplot")
end
```

```julia
┌ Info: Correlation Matrix
│   corr_matrix =
│    6×6 Matrix{Float64}:
│     1.0         0.878214   0.240162   0.126952   0.267604   0.0864104
│     0.878214    1.0       -0.253355  -0.247737  -0.160763   0.154384
│     0.240162   -0.253355   1.0        0.759608   0.867571  -0.138572
│     0.126952   -0.247737   0.759608   1.0        0.345521   0.233941
│     0.267604   -0.160763   0.867571   0.345521   1.0       -0.36578
└     0.0864104   0.154384  -0.138572   0.233941  -0.36578    1.0
```
